---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
    Author: Ramamurthi Sridharan
---
## Loading and preprocessing the data
## sum steps data by day - a vector
##  Plot as a histogram
##  Summary (resulting data)
```{r read data}
data <- read.csv(unzip("activity.zip","activity.csv"))
nrow(data)
ncol(data)
summary(data)
```
## summary of data indicate there are 2304 NA's in the data set

##  Compute the daily sum of total steps and plot a histogram

```{r determine sum}
y <- tapply(data$steps, data$date, sum)
y
hist(y, breaks =100)
```

## What is mean total number of steps taken per day?

```{r determine mean of the sum}
mean.total = mean(y, na.rm = TRUE)
mean.total
```

## What is the average daily activity pattern?

```{r daily average per interval}
daily.int.mean = NULL
daily.int.mean <- tapply(data$steps, data$interval, mean, na.rm = TRUE)
daily.int.mean
max(daily.int.mean)
plot(daily.int.mean, type = "l", xlab = "Interval", ylab = "daily actvity (means steps/ interval)")
```

## Imputing missing values 
## daily mean values for corresponding interval is used to replace the NA's

```{r remove NAs} 
data[is.na(data)] <- tapply(data$steps, data$interval, mean, na.rm = TRUE)
z <- tapply(data$steps, data$date, sum)
z
hist(z, breaks =100)
```


## Are there differences in activity patterns between weekdays and weekends?
